%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Latex File for CV and Resume
% Last edit 25/03/2019 
% Saket Adhau
% saketadhau@live.com
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{resume}
\usepackage{ragged2e}
\usepackage{calc}
\usepackage{comment}
\usepackage{wasysym}
\usepackage{array}
\usepackage{marvosym}
\usepackage{tabu}
\usepackage{fontawesome}
\makeatletter
\usepackage{amssymb}
\usepackage[bottom]{footmisc}
\usepackage{relsize}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{marvosym}
% Software
\newcommand{\mt}{\textsc{MATLAB}}
\newcommand\cpp{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\relsize{-3}{\textbf{++}}}}
\newcommand\cp{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\relsize{-3}{\textbf{}}}}
\newlength{\bibhang}
\setlength{\bibhang}{1em} 
\newlength{\bibsep}
{\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
{\begin{enumerate}{}{
			\setlength{\leftmargin}{\bibhang}
			\setlength{\itemindent}{-\leftmargin}
			\setlength{\itemsep}{\bibsep}
			\setlength{\parsep}{\z@}
			\setlength{\partopsep}{0pt}
			\setlength{\topsep}{0pt}}}
	{\end{enumerate}\vspace{-.6\baselineskip}}
\makeatother
\reversemarginpar
\usepackage[paper=letterpaper,
marginparwidth=0.05in,    
marginparsep=.05in,    
margin=0.9in,             
includemp]{geometry}
\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
{0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}
	\parbox{4in}{\, \hfill 
		\arabic{page} of \protect\pageref*{LastPage} % +LP
		\hfill \,}}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}

\newcommand{\makeheading}[2][]
{\hspace*{-\marginparsep minus \marginparwidth}
	\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}
		{\large \bfseries #2 \hfill #1}\\[-0.15\baselineskip]
		\rule{\columnwidth}{0pt}
\end{minipage}}

% The section headings
%
% Usage: \section{section name}
\renewcommand{\section}[1]{\pagebreak[3]%
	\hyphenpenalty=1000%
	\vspace{1.3\baselineskip}%
	\phantomsection\addcontentsline{toc}{section}{#1}%
	\noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright 
	#1}}}
	\vspace{-\baselineskip}\par}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
{\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
	\vspace{-.5\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
{\begin{list}{#1}{%
			\setlength{\partopsep}{0pt}%
			\setlength{\topsep}{0pt}}}
	{\end{list}\vspace{-.5\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
{\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
	{\end{itemize}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
{\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
	{\end{itemize}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

% Uses hyperref to link DOI
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}


\providecommand*\url[1]{\href{#1}{#1}}

\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}


\providecommand*\email[1]{\href{mailto:#1}{#1}}
\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		\TeX}}
\providecommand\Matlab{\textsc{Matlab}}

%-------------------------End Helper Commands----------------------------------%

%-------------------------Begin CV Document------------------------------------%
\begin{document}
	\makeheading{    
		\begin{center}
			\LARGE{SAKET ADHAU \\ \small{Master of Technology - Instrumentation and Control}} 
		\end{center}
		\newlength{\rcollength}\setlength{\rcollength}{2.35in}%
\begin{center}
	\normalsize{\textnormal{
			\Letter~Department of Instrumentation and Control,\\ College of Engineering, Pune - 411005, INDIA\\				
			\href{https://saketadhau.netlify.com/} 
			{\Mundus~saketadhau.netlify.com}
			\href{https://www.linkedin.com/in/saketadhau/} 
			{\faLinkedinSquare~saketadhau}  \\
			\Email~{\email{adhauss17.instru@coep.ac.in}}
			\Mobilefone~(+91) 9421837806}}\vspace{-8mm}
\end{center}
	}\vspace{2mm}

%------------------------------------------------------------------------------%.
\begin{rSection}{Education}
{\bf{Master of Technology, Instrumentation and Control} \hfill {\textit{Aug'17--June'19}}}
\begin{outerlist}
	\item[-]  \href{http://www.coep.org.in/} {College of Engineering Pune, India}
	\begin{innerlist}
		\item[--] Thesis Title: \textit{Learning Based Model Predictive Control}
		\item[--] Supervisor: \href{http://www.coep.org.in/mycoep/dnsinstrucoepacin} {Prof. Dayaram Sonawane}
		\item[--] CGPA: $ 7.89 $
	\end{innerlist}
\end{outerlist}
\vspace{.1in}
\textbf{{Bachelor of Engineering, Instrumentation and Control}} \hfill \textit{\textbf{Aug'13--June'17}}
\begin{outerlist}
%	\item \href{http://www.gcoeara.ac.in/} {Government College of Engineering and Research, Avasari Kh., Pune.}
	\item[-]  \href{http://www.unipune.ac.in/} {University of Pune, India}	
	\begin{innerlist}
		\item[--] Project Title: \textit{System Identification and PID Control of PMDC Motor using \mt~and LabVIEW}
		\item[--] Supervisor: \href{http://www.gcoeara.ac.in/Instrumentation-control-about-us.php} {Dr. Milind Bongulwar}
		\item[--] Mention:  First Class with Distinction $ \vert $ Percentage: $69.67$
	\end{innerlist}
\end{outerlist}
\end{rSection}
\vspace{5mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Publications}
	\textbf{Articles in international conferences}\\
	\textbf{2019}
	\begin{outerlist}
	\item \textbf{Adhau S.}, Patil S., Ingole D., and Sonawane D., ``\href{https://www.researchgate.net/publication/331225239_Implementation_and_Analysis_of_Nonlinear_Model_Predictive_Controller_on_Embedded_Systems_for_Real-Time_Applications}{Implementation and Analysis of Nonlinear Model Predictive Controller on Embedded Systems for Real-Time Applications}'', \textit{in Proceedings of the $ 17^{th} $ European Control Conference (ECC'$19 $)}, IFAC and IEEE, Naples, Italy, $ 2019 $.
	\end{outerlist}

	\textbf{2018}
	\begin{outerlist}
	\item \textbf{Adhau S.}, Phalke K., Nalawade A., Ingole D., Patil S., Sonawane D., ``\href{https://saketadhau.netlify.com/publication/icc/icc.pdf}{Implementation and Analysis of Offset-Free Explicit Model Predictive Controller on FPGA}'', \textit{in Proceedings of $ 5^{th} $ Indian Control Conference}, IEEE, Delhi, India, $ 2018 $.

	\item \textbf{Adhau S.}, Dani S., Ingole D., and Sonawane D., ``\href{https://saketadhau.netlify.com/publication/i2ct/i2ct.pdf}{Embedded Model Predictive Control on Low-Cost Low-End Microcontroller for Motor Speed Control}'', \textit{in Proceedings of International Conference for Convergence in Technology (I$ 2 $CT)}, IEEE, Mangalore, India, $ 2018 $.	
	\end{outerlist}
\end{rSection}	
\vspace{5mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Research Interests}
\begin{tabu} to 1\textwidth {  X[l]  X[l]  }
1. Machine learning for MPC & 4. Optimization  \\ 
2. Nonlinear Model predictive control & \\
3. Embedded systems & \\
\end{tabu}
\end{rSection}
\vspace{5mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Projects}
	\begin{outerlist}
		\item \textbf{Deep Neural Networks based Linear MPC} 
		\begin{innerlist}
			\item[--] Trained highly nonlinear and linear models using neural networks, to mimic the original model.
			\item[--] Neural networks were trained to behave as Linear model predictive controller to reduce the online optimization and guarantee safety. 
			\item[--] The designed neural network was also implemented on ARM Cortex-M$ 3 $ to prove the usability in embedded devices.
		\end{innerlist}
	
		\item \textbf{Implementation of nonlinear MPC on ARM Cortex-M$ 3 $ and FPGA} 
		\begin{innerlist}
			\item[--] Successfully implemented nonlinear MPC on for the first time ARM Cortex-M$ 3 $ and FPGA using GRAMPC and ACADO toolkit
			\item[--] The performance of NMPC controller was rigorously tested using HIL simulations in \mt 
			\item[--] Designed framework for easy implementation of NMPC on micro-controllers and FPGA.
		\end{innerlist}
	
		\item \textbf{Linear and explicit MPC on ARM Cortex-M$ 3 $ and FPGA} 
		\begin{innerlist}
			\item[--] Implemented Interior Point Method, Active Set Method and KWIK Algorithm for linear MPC on Arm Cortex-M$3$
			\item[--] Validated the designed MPC on DC motor using HIL simulation for real-time using Simulink coder.
			\item[--] Implemented Explicit MPC using MPT toolbox, Hybrid toolbox and MATLAB based toolbox on micro-controllers and validated the same on actual plant
			\item[--] The same framework was also validated and detailed analysis were carried out on FPGA Zedboard.
		\end{innerlist}
	
		\item \textbf{Auto-tuning of PID controller using optimization method} 
		\begin{innerlist}
			\item[--] Evaluated optimization algorithm SQP for auto-tuning of PID controller 
			\item[--] Verified values of $ K_{p}, \; K_{i} $ and $ K_d $ parameters using run-time optimization in \mt/Simulink.
		\end{innerlist}	
	
		\item \textbf{Parameter Estimation and Position control of PMDC motor} 
		\begin{innerlist}
			\item[--] Validated PMDC motor model using parameter estimation
			\item[--] Implemented SQP algorithm in \mt~for parameter estimation
			\item[--] Implemented and tested PID controller for position and speed control on ARM Cortex-M$ 3 $ micro-controller
		\end{innerlist}	
	
		\item \textbf{System Identification and PID Control} 
		\begin{innerlist}
			\item[--] System identification for an unknown DC motor was done using System Identification toolbox of \mt
			\item[--] Verified the system by passing through various linear and non-linear signals for accurate system model
			\item[--] PID tuning using Zeigler Nicholas and Cohen-Coon methods for speed control of the DC motor using identified state-space model 
			\item[--] Implemented PID controller on $8$-bit micro-controller using plain~\cp~code, \mt~based embedded coder and in LabVIEW using toolbox for VISA protocol.
		\end{innerlist}		
%		\item \textbf{Signal conditioning for RTD sensor} 
%		\begin{innerlist}
%			\item[--] Signal conditioning was done for industrial grade RTD and the temperature was shown using $8051$ microcontroller.
%			\item[--] Done as a part of mini-project of undergraduate courses.
%		\end{innerlist}	
%		\item \textbf{\mt~based ECG using Arduino board} 
%		\begin{innerlist}
%			\item[--] real-time ECG was acquired, conditioned using arduino and ADC.
%			\item[--] \mt~was used for interface to arduino board over serial and as a GUI.
%		\end{innerlist}		
	\end{outerlist}
\end{rSection}
\vspace{8mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Internship Experience}
	{\textbf{Bosch Chassis Systems India Pvt. Limited, Chakan, Pune.} \hfill \textit{\textbf{June'15 - July'15}}}
	\begin{outerlist}
		\item  Worked with the TeF department towards maintenance and predictive safety standards.
		\item  Carried out analysis of Mean Time To Repair (MTTR) and Mean Time Between Repair (MTBR) on the assembly lines (NOAH, Line $51$, TMC line).
		\item  Studied advanced braking systems like Anti-lock brake systems (ABS) and electronic stability program (ESP).
		\item  Studied various kinds of braking systems viz. Mascular-energy braking, power assisted braking system, parking brake system for passenger cars.
		\item  Studied the working of brake boosters, Tandem master cylinder, design of braking system, brake pedal and braking components.
	\end{outerlist}
\end{rSection}
\vspace{8mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Positions of Responsibility}
	\begin{outerlist}
		\item \textbf{Co--ordinator for $ 3^{rd} $ Winter School.} \hfill \textit{\textbf{Dec'18}} 
			\begin{innerlist}
				\item[--] Served as convener and co--ordinator of \textbf{$ 3^{rd} $ Winter School on Optimization and Optimal Control -- A Data--based Approach} at Embedded Systems Lab, COEP.
				\item[--] Responsible for organization and management of  more than $50$ candidates.
			\end{innerlist}
		\item \textbf{Teaching Assistant.} \hfill \textit{\textbf{July'18--Dec'18}}
			\begin{innerlist}
				\item[--] Served as TA for \textbf{Microcontroller Techniques and Its Applications} for undergraduate students.
				\item[--] Responsible for conducting practicals and tutorials for a class of 60 students.
			\end{innerlist}	
		\item \textbf{Teaching Assistant.} \hfill \textit{\textbf{Dec'17}}
			\begin{innerlist}
				\item[--] Served as TA for \textbf{Embedded System Design} which was a special course conducted embedded systems lab, COEP.
				\item[--] Responsible for conducting practicals and tutorials for a class of 20 students.
			\end{innerlist}	
		\item \textbf{Graduate Class Representative} \hfill \textit{\textbf{Aug'17--June'19}}
			\begin{innerlist}
				\item[--] Served as Class Representative (CR) for masters student, Biomedical engineering $ 2019  $ batch.
				\item[--] Responsible for various activities, organization and management of students.
			\end{innerlist}		
		\item \textbf{Students Placement Cell -- Co--ordinator} \hfill \textit{\textbf{Aug'16--June'17}}
			\begin{innerlist}
				\item[--] Co--ordinator at Training and Placement cell in college for undergraduate students. 
				\item[--] Organizing various training and placements programs for a class of 60 students.
			\end{innerlist}	
		\item \textbf{Technical Event Head -- Micromania } \hfill \textit{\textbf{Sep'16}}
			\begin{innerlist}
				\item[--] Event head for annual technical fest of the college.
				\item[--] Responsible for conduct of various events and workshops under the technical event.
		\end{innerlist}		
	\end{outerlist}
\end{rSection}
\vspace{14mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Awards and Funding}
\begin{outerlist}
	\item Project accepted for oral presentation in \textbf{\mt ~Expo'19.} \hfill \textit{\textbf{May'19}}
	\item Student support program for Indian Control Conference -- IIT Delhi. \hfill \textit{\textbf{Jan'19}}
	\item Xilinx University Program for researchers  -- Pynq development board and software. \hfill \textit{\textbf{Sep'18}}
\end{outerlist}
\end{rSection}
\vspace{20mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Skills \& Interests}
%\vspace{-.15in}
\begin{outerlist}
	\item \textbf{General} 
		\begin{innerlist}
			\item[--] Nonlinear optimization, model-based control, nonlinear dynamic system modeling. 
		\end{innerlist}
	\item \textbf{Programming languages}
		\begin{innerlist}
			\item[--] \cp, \cpp, HTML, Python.
		\end{innerlist}
	\item \textbf{Tools}
		\begin{innerlist}
			\item[--] \mt/Simulink, \LaTeX, TikZ, Inkscape, Microsoft office suite.
		\end{innerlist}
	\item \textbf{Development}
		\begin{innerlist}
			\item[--] Atmel Studio, Vivado, MPLAB X,  HDL coder, LabView, Arduino IDE, Linux.
		\end{innerlist}
	\item \textbf{Toolboxes}
		\begin{innerlist}
			\item[--] Protoip, MPT toolbox, ACADO Toolkit, CasADi, FORCES, GRAMPC.
		\end{innerlist}
	\item \textbf{Version control tools}
		\begin{innerlist}
			\item[--] GitHub, GitLab, Bitbucket.
		\end{innerlist}
\end{outerlist}
\end{rSection}
\vspace{8mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Training}
	\begin{outerlist}
		\item $3$ days workshop on Tiva C and MSP$ 430 $ based Embedded System Design.\hfill \textit{\textbf{March'19}}
		\item Winter School on Optimization and Optimal Control - A Data-based Approach. \hfill \textit{\textbf{Dec'18}}		
		\item One month Certificate course on embedded systems design. \hfill \textit{\textbf{Dec'17}}		
		\item Certificate course on Ethical hacking, COEP, India \hfill \textit{\textbf{Sep'16}}
		\item \mt~\& Simulink for engineers, one month training at COEP. \hfill \textit{\textbf{Dec'15}}		
	\end{outerlist}
\end{rSection}
\vspace{8mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Personal Details}
%	\vspace{-.1275in}
	\begin{outerlist}
		\item Full Name: Saket Sunil Adhau
		\item Citizenship: Indian
		\item Date of Birth: 29 May 1995 
	\end{outerlist}
\end{rSection}
\vspace{8mm}
%------------------------------------------------------------------------------%
\begin{rSection}{Referees}
\begin{tabu} to 1\textwidth {  X[l]  X[l]  }
	\href{https://scholar.google.co.in/citations?user=sKwGRiYAAAAJ}{Prof. Dayaram Sonawane}  &  \href{https://scholar.google.co.in/citations?user=FjehteAAAAAJ}{Dr. Deepak Ingole} \\
	HOD \& In-charge,  \href{http://www.coepembeddedlab.com/}{Embedded Systems Lab}   & Postdoctoral Researcher \\
	Department of Instrumentation and Control,   & \href{https://www.universite-lyon.fr/}{University of Lyon}, \href{https://www.ifsttar.fr/en/welcome/}{IFSTTAR}, \href{https://www.entpe.fr/en}{ENTPE} \\ 
	\href{http://www.coep.org.in/}{College of Engineering, Pune} -- 411005, INDIA &  Vaulx-en-Velin -- 69120, FRANCE\\
	\Email{~\email{hod.instru@coep.ac.in}}   & 	\Email{~\email{deepak.ingole@ifsttar.fr}} \\
	\href{http://www.coep.org.in/mycoep/dnsinstrucoepacin} 
	{\Mundus~Homepage} & 	\href{http://www.ingoledeepak.wordpress.com} 
	{\Mundus~Homepage}  \\
\end{tabu}
\end{rSection}
\end{document}
%-----------------------------------------------------------------------------%